Online {\IterComp}

### 2017-09-13 motivation.tex
fix

The blue bars in Figure~\ref{fig:motivation-online} show a different approach where during \itercomp the speedup of
each optimization sequence is again measured on a small input subset but this subset changes for every optimization
sequence. This is similar to how online \itercomp would have to work, using each input only once. This might introduce
errors, since the speedups we measure for each optimization sequence are not strictly comparable, they are measured on
different workloads. But in the end the histogram shows that being able to test more inputs allows us to make better
informed decisions. This approach never degrades performance compared to \textt{-O3}, performance varies less, and on
average is 13\% better than the offline approach.

>>>>

The blue bars in Figure~\ref{fig:motivation-online} show a different approach where during \itercomp the speedup of each optimization
sequence is again measured on a small input subset but this subset changes for every optimization sequence. This is similar to how online
\itercomp would have to work, using each input only once. This might introduce errors, since the speedups we measure for each optimization
sequence are not strictly comparable, they are measured on different workloads. But in the end the histogram shows that being able to test
more inputs allows us to make better informed decisions. This approach never degrades performance compared to \texttt{-O3}, performance
varies less, and on average is 13\% better than the offline approach.
